Chasing \rainbows{} with the Habitable Worlds Observatory

### 2023-02-27 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure*}%[t]
   \centering
   \includegraphics[width=0.99\textwidth]{figures/orb-grid.pdf}
   \caption{
        The scattering phase angles accessible to a direct imaging mission can be limited by orbital inclination or by the coronagraphic inner working angle. 
        If the orbital inclination is close to face-on (top panels) then the scattering phase angles probed throughout an orbit are limited by inclination; for circular orbits accessible scattering phases are $\phi \in 90^\circ \pm i$. 
        For orbital inclinations close to edge-on (bottom panels) the planet goes through all phases, but the scattering phase angles near 0$^\circ$ and 180$^\circ$ are not accessible due to obscuration by the coronagraph mask; for circular orbits, the accessible scattering phases are $\phi \in 90^\circ \pm \arcsin({\rm IWA}\cdot d_*/a)$.
    }
    \label{fig:orb-grid}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/scatterplot.pdf}
    \caption{
        \todo{Are those the results we obtained for circular, edge-on orbits? 
        We should clarify this also in the figure caption.}
        \todo{The figure is currently broken because showyourwork is using matplotlib 3.4 --- I (Timmy) can debug this if it turns out we cannot use a newer version of matplotlib, but if updating to 3.7 is okay, I will save myself the efforts.}
        Scatter plot at 3 $\lambda/D$ for the target sample, showing stellar effective temperature and stellar distance. 
        The size of the points represents the angular separation of the star and planet in milliarcseconds as presented in the target list. 
        The colour of the points shows the atmospheric phenomenon that can be detected with darker colours, including all lighter (yellow) colour phenomenon. 
        Thus, dark blue points are systems which have the most key features, as systems in which the angles required to see the rainbow are probed will also have the angles required to see the Rayleigh scattering probed.
    }
    \label{fig:scatterplot}
    \script{create-scatterplot.py}
\end{figure*}

>>>>

\begin{figure*}%[t]
   \centering
   \includegraphics[width=0.99\textwidth]{figures/orb-grid.pdf}
   \caption{
        The scattering phase angles accessible to a direct imaging mission can be limited by orbital inclination or by the coronagraphic inner working angle. 
        If the orbital inclination is close to face-on (top panels) then the scattering phase angles probed throughout an orbit are limited by inclination; for circular orbits accessible scattering phases are $\phi \in 90^\circ \pm i$. 
        For orbital inclinations close to edge-on (bottom panels) the planet goes through all phases, but the scattering phase angles near 0$^\circ$ and 180$^\circ$ are not accessible due to obscuration by the coronagraph mask; for circular orbits, the accessible scattering phases are $\phi \in 90^\circ \pm \arcsin({\rm IWA}\cdot d_*/a)$.
    }
    \label{fig:orb-grid}
    \script{plot-orb-grid.py}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/scatterplot.pdf}
    \caption{
        \todo{Are those the results we obtained for circular, edge-on orbits? 
        We should clarify this also in the figure caption.}
        Scatter plot at 3 $\lambda/D$ for the target sample, showing stellar effective temperature and stellar distance. 
        The size of the points represents the angular separation of the star and planet in milliarcseconds as presented in the target list. 
        The colour of the points shows the atmospheric phenomenon that can be detected with darker colours, including all lighter (yellow) colour phenomenon. 
        Thus, dark blue points are systems which have the most key features, as systems in which the angles required to see the rainbow are probed will also have the angles required to see the Rayleigh scattering probed.
    }
    \label{fig:scatterplot}
    \script{create-scatterplot.py}
\end{figure*}
